---
title: "Addressing Issues with an InternalFunction and External Package Environment"
author: "JJB"
date: "3/20/2019"
output: html_document
---

OP: https://stackoverflow.com/questions/55265496/calling-numderivhessian-with-multiple-parameter-objective-function-in-rcpp

Problem: Environment not found / reduction issue.

Couple of quick notes:

- Try the implementation in _R_ and then move it to _C++_.
    - Provides a reference point and makes sure that everything works as intended.
- Search paths and names matter
    - Explicitly load `numDeriv` package before compiling.
    - Respect capitalization `X` vs. `x`.
- Ensure output types are accurate
    - From  [`?numDeriv::hessian`](https://cran.r-project.org/web/packages/numDeriv/numDeriv.pdf#page=8), the output type is an **N** x **N** `Rcpp::NumericMatrix` instead of `Rcpp::List`.
    
```{r, error = TRUE}
k = 2
k_dimensional = function(x, N) {
 x ^ N 
}

numDeriv::hessian(k_dimensional, x = rep(1, k), N = 3)
```

Improved _C++_ implementation following notes:


```{Rcpp}
#include <Rcpp.h>

double k_dimensional_cpp(Rcpp::NumericVector x, double N){
// ^^ Change return type from NumericVector to double

  // Speed up the process by writing the _C++_ loop
  // instead of relying on Rcpp sugar.
  double total = 0;
  for(int i = 0 ; i < x.size(); ++i) {
      total += std::pow(x[i], N);
  }
  
  // Return the accumulated total
  return total;
}

// [[Rcpp::export]]
Rcpp::NumericMatrix call_hess_cpp(double K) {
    
  // Ensure that numDeriv package is loaded prior to calling this function
  Rcpp::Environment numDeriv("package:numDeriv");
  Rcpp::Function hessian = numDeriv["hessian"];
  
  double param = 3;
  Rcpp::NumericVector x = Rcpp::rep(1.0, K);
  
  // Switched from Rcpp::List to Rcpp::NumericMatrix
  Rcpp::NumericMatrix hessian_results = 
  hessian(
    Rcpp::_["func"] = Rcpp::InternalFunction(k_dimensional_cpp),
    Rcpp::_["x"] = x,    // use lower case x to match function signature.
    Rcpp::_["N"] = param
  );

  // Return the calculated hessian
  return hessian_results;
}
```

```{r}
call_hess_cpp(2)
```

